---
output: github_document
---

<script src="https://cdn.mathjax.org/mathjax/latest/MathJax.js?config=TeX-AMS-MML_HTMLorMML" type="text/javascript"></script>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# FLAMES

<!-- badges: start -->
<!-- [![CRAN status](https://www.r-pkg.org/badges/version/FLAMES)](https://cran.r-project.org/package=FLAMES) -->
[![Travis build status](https://travis-ci.org/DouglasMesquita/FLAMES.svg?branch=master)](https://travis-ci.org/DouglasMesquita/FLAMES)
<!-- [![Codecov test coverage](https://codecov.io/gh/DouglasMesquita/FLAMES/branch/master/graph/badge.svg)](https://codecov.io/gh/DouglasMesquita/FLAMES?branch=master) -->
<!-- badges: end -->

## Overview

FLAMES: Flexible Link function with AssyMptotES is a package able to fit binary regression under several link functions and two possible assymptotes parameters, c and d, in the form 

<center>
![equation](http://latex.codecogs.com/gif.latex?p_i%20=%20c%20+%20(d-c)F_v(%5Ctext{X}%5Cbeta)) 
</center>

## Installation

```{r eval = FALSE}
# Install from CRAN (when available)
install.packages("FLAMES")
# Or the development version from GitHub
# install.packages("devtools")
devtools::install_github("DouglasMesquita/FLAMES")
```

## Usage

`library(FLAMES)` will load **mcmc_bin**, a function to fit binary regression models. The user can choose for MCMC based on ARMS or Metropolis Hastings algorithms. Also it is possible to fit **logit**, **probit**, **cauchit**, **cloglog**, **loglog** and **robit** regressions.

See `?mcmc_bin` for examples.
